---
title       : Coursera Developing Data Products Slidify Project
subtitle    : Saturday, April 25, 2015
author      : Matías Alfredo Morales Armijo
job         : 
framework   :  io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap,interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/nvd3]}
---

## The Project

This is my reproducible pitch presentation, where I describe what I did in my simple app project.
This project works with a matrix of incomes and expenses of three years (2012,2013,2014) of a company. This data matrix was invented. This shiny calculates the utility of the year selected by the user.
Utility is the difference between income and expense in a month.
$$Utility (U)=Income (I)-Expense (E)$$


--- 

## The Dataset column names (Example one year)
```{r block1}
data<-data.frame(year=c(2014,2014,2014,2014,2014,2014,2014,2014,2014,2014,2014,
2014,2013,2013,2013,2013,2013,2013,2013,2013,2013,2013,2013,2013,2012,2012,
2012,2012,2012,2012,2012,2012,2012,2012,2012,2012),month=c(1,2,3,4,5,6,7,8,9,10
,11,12,1,2,3,4,5,6,7,8,9,10,11,12,1,2,3,4,5,6,7,8,9,10,11,12),
incomes=c(500,1000,1100,1200,1350,900,800,900,1000,1150,1200,1300,
600,650,700,710,720,730,750,710,720,730,740,750,600,650,700,710,720,
730,750,710,720,730,740,750),expenses=c(20,30,40,50,60,70,65,60,54,77,
87,88,50,50,50,50,50,50,65,65,70,70,70,70,60,60,65,56,58,77,70,65,72,73,71,70))
head(data)
```
 

---

## How it works

 1. The user select a year    
 2. In all cases above, when the user make a choice, the plot is updated with the year selected by the user.
 2. The Platform calculates Utility from year selected
 3. The user can choise between several graphical options: 
  Incomes in the selected year.
  Compare incomes/expenses 
  Utility in the year

Take this amazing experience going to: https://matiasmorales.shinyapps.io/project/


---

## Plot Sample
```{r echo = F, results = 'asis'}
require(rCharts)
 n1 <- nPlot(incomes ~ month, group = "year", data = data, type = "multiBarChart")
  
  n1$addParams(width = 600,height = 350, dom = 'chart4')
n1$print('chart4')




```
